%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Machine Learning Engineer (Master's Thesis)} % Job title
    {IBM Research} % Organization
    {Zürich, Switzerland} % Location
    {May. 2025 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Investigating aggressive model compression for on-premise deployment of custom LLMs for clients.}
        \item {Created a novel quantization framework utilizing <5 full precision weights with ternary quantization.}
        \item {Evaluated the effectiveness of the framework on various models, involving setting up efficient fine-tuning and evaluation pipeline.}
      \end{cvitems}
    }

  \cventry
    {Software Engineer (Part-time)} % Job title
    {IVIA Lab - ETH Zürich} % Organization
    {Zürich, Switzerland} % Location
    {Aug. 2024 - May 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built backend capabilities and set up devOps pipeline from the ground up for a system to connect students with industry partners for \\
        thesis/internships.}
        \item {Enabled authentication and authorization including SSO for ETH users through Keycloak integration across the stack.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Qatar Computing Research Institute} % Organization
    {Doha, Qatar} % Location
    {Oct. 2021 - Sep. 2023} % Date(s)
    {
      \begin{cvitems}
        \item {Built MVP solutions for various commercialization efforts of research projects at QCRI.}
        \item {Mentored and managed 6 interns.}
        \renewcommand{\labelitemi}{}
        \item {\hspace{-3.0mm}\underline{{\href{https://allama.qcri.org}{Allama}}} - GPT based chatbot using Langchain on Qatar ministry data}
        \renewcommand{\labelitemi}{\bullet}
        \item {Set up a pipeline to automatically crawl, parse, embed, and populate data into vector DB to keep chatbot up to date.}
        \item {Configured CI/CD using Azure Pipelines and Docker Swarm.}
        \renewcommand{\labelitemi}{}
        \item {\hspace{-3.0mm} \underline{{\href{https://judo.qcri.org}{JUDO}}} - Web-based interactive traffic microsimulation based on SUMO}
        \renewcommand{\labelitemi}{\bullet}
        \item {Built a web-based visualization system for SUMO simulations, including various performance critical features such as visual clustering
        of vehicles, frame dropping, and intelligent memory management to avoid buffering, taking fps from <3 to 30 when scaling to over 1 million vehicles.}
        \item {Dockerized \underline{\href{https://github.com/qcri/qarsumo}{QarSUMO}} and created an API to access it to easy deployment and scalability.}
        \renewcommand{\labelitemi}{}
        \item {\hspace{-3.0mm}\underline{{\href{https://siha.qcri.org}{SIHA}}} - platform to extract, unify, and provide health data from various wearable devices}
        \renewcommand{\labelitemi}{\bullet}
        \item {Took ownership of the SIHA mobile app, migrating it to null-safety and BLOC architecture pattern, updated screen designs to match new brand identity, and developed new Team Competitions feature.}
        \item {Implemented a YAML interface for \underline{\href{https://github.com/qcri/tasrif}{TASRIF}}, an open-source tool for processing time-series data.}
        \item {Created an on-premise deployment script for SIHA that pulls all the relevant images from MS azure, allowing deployment without loading sensitive code.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Quickbyte} % Organization
    {Doha, Qatar} % Location
    {Dec. 2020 - June. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Part of the founding engineering team at Quickbyte, a food delivery startup in Qatar.}
        \item {Built an admin dashboard for managing restaurants and menus using React and NodeJS to streamline previously manual processes, removing developer interventions entirely.}
        \item {A/B tested and implemented group ordering and chat based ordering features.}
        \item {Created indexes in MongoDB to optimize DB queries, reducing query times by 12x.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Engineer} % Job title
    {Computional Biology Lab, Carnegie Mellon University} % Organization
    {Doha, Qatar} % Location
    {Oct. 2018 - Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a dashboard for visualizing data generated from breast cancer databases using React, NodeJS and MongoDB fulfilling a deliverable for the lab's research grant.}
        \item {Compiled a database on Minor Intron Containing Genes (MIGs) to help investigate their role in regulating oncogenes, including computational prediction of how minor intron retention impacts protein synthesis using an automated process.}
        \item {Developed an RNA-Seq pipeline that performs read alignment, mapping, and calculates gene abundance for analyzing lab-generated data.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
