% !TeX root = ../resume.tex
%!TEX root = ../resume.tex
%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Leadership}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Head Orientation Counselor} % Affiliation/role
    {Carnegie Mellon University in Qatar} % Organization/group
    {Doha, Qatar} % Location
    {Jun. 2020 - Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Designed and delivered online orientation for 130 incoming students, centralizing resources for academic and campus life.}
        \item {Led the first cross-campus orientation event to facilitate broader Education City community building, partnering with 3 other universities.}
        \item {Introduced Tartan Bridge Buddies initiative: 1:1 pairing between first-years and upperclass mentors.}
        \item {Planned and facilitated training for 70 orientation volunteers focused on effective communication and student support.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Trip Leader for Environment Service Project} % Affiliation/role
    {Carnegie Mellon University in Qatar} % Organization/group
    {Doha, Qatar} % Location
    {Sep. 2019 - Mar. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Managed $\sim$ \$22k budget; led 9-student service-learning project under Tartans Without Borders initiative.}
        \item {Drove campus engagement through outreach campaigns; achieved 60 applications (record for TWB).}
        \item {Led pre-departure training on ethical volunteering and teaching practices.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
  {CS Society President} % Affiliation/role
  {Carnegie Mellon University in Qatar} % Organization/group
  {Doha, Qatar} % Location
  {Aug. 2019 - May. 2020} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Hosted alumni talks and social events to strengthen the CS community.}
      \item {Co-led a GameDev hackathon in partnership with alumni.}
    \end{cvitems}
  }
    
%---------------------------------------------------------
\end{cventries}
