%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Submitted to EMNLP for review. Preprint at \url{https://arxiv.org/pdf/2405.20318}} % link/venue
    {Quriosity: Analyzing Human Questioning Behavior
and Causal Inquiry through Curiosity-Driven Queries} % Title
    {} % Location
    {2025} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Investigated human querying behavior across different channels including Human to Search Engines, LLMs, and other
        humans.}
        \item {Analyzed causal nature of these queries and trained a router based system of fine-tuned models to answer causal queries.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Codebase available at \url{https://github.com/mak2508/recurrent-lop}} % Role
    {Loss of Plasticity in Recurrent Models} % Title
    {} % Location
    {2025} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Explored the existence of Loss of Plasticity in Recurrent models and evaluated the effectiveness of mitigation strategies.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
{Codebase available at \url{https://github.com/mak2508/recurrent-lop}} % Role
{Exploiting Backdoor Vulnerabilities in Communication Based Multi-Agent Reinforcement Learning} % Title
{} % Location
{2024} % Date(s)
{
  \begin{cvitems} % Description(s)
    \item {Explored backdoor vulnerabilities in communication based CMARL systems, specifically a traffic environment.}
    \item {Showed that a trigger can be inserted inside a message sent by agents in communication-based MARL.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Codebase available at \url{https://github.com/mak2508/prob_rsa}} % Role
{A Probalistic Implementation of Rational-Speech-Act Framework for Presupposition} % Title
{} % Location
{2024} % Date(s)
{
  \begin{cvitems} % Description(s)
    \item {Developed the first probabilistic Rational Speech Act (RSA) model of presupposition triggering using the Pyro prob-
    abilistic programming framework, simplifying posterior distribution computations for more complex interactions.}
    \item {Formally proving a faster linear runtime, compared to previous exponential runtime.}
  \end{cvitems}
}

%---------------------------------------------------------
\end{cventries}
